Phase Curves of WASP-103b

### 2017-09-20 ms.tex
data reduction

\section{Observations and Data Reduction}
We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m. We also reduced two additional WFC3 secondary eclipse observations from \HST Program FIXME (PI: M. Zhao).

\subsection{\HST/WFC3}
The \emph{HST} observations consisted of two visits on 26-27 February and 2-3 August 2015. Each visit was 15 orbits in duration and spanned 23 hours. We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution. The remainder of the orbit consisted of time-series spectroscopy with the G141 grism and the 256 x 256 pixel subarray. We used the SPARS10/NSAMP = 15 read-out mode, which has an exposure time of 103 seconds. The exposures were taken with the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector to diminish overhead time. The scan height was 25 pixels and the peak counts were 30k photoelectrons per pixel. We collected a total of 18 spatial scan exposures per orbit.  Our analysis also uses secondary eclipse observations of WASP-103b from \emph{HST} program 13660 (PI: M. Zhao), which obtained time series spectroscopy with the G141 grism using a similar setup. Further description of the observational design for this program is given in Star Cartier (in prep).

We reduced the data from both programs using a custom pipeline that has been developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}. The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:

@@

\section{Light Curve Analysis}

>>>>

\section{Observations and Data Reduction}
We observed two full-orbit phase curves of WASP-103b with \HST/WFC3 and one each with \Spitzer/IRAC at 3.6 and 4.5 $\mu$m. We also reduced two additional WFC3 secondary eclipse observations from \HST Program 13660 (PI: M. Zhao).

\subsection{\HST/WFC3}
The \emph{HST} observations consisted of two visits on 26-27 February and 2-3 August 2015. Each visit was 15 orbits in duration and spanned 23 hours. We took a direct image of the star with the F126N filter at the beginning of each orbit to determine the wavelength solution zero-point. The remainder of the orbit consisted of time-series spectroscopy with the G141 grism ($1.1 - 1.7$ $\mu$m) and the 256 x 256 pixel subarray. We used the SPARS10/NSAMP = 15 read-out mode, which has an exposure time of 103 seconds. To optimize the duty cycle of the observations, we used the spatial scan observing mode with a scan rate of 0.03"/s, alternating between forward and backward scanning on the detector. The scan height was 25 pixels and the peak counts were 35k photoelectrons per pixel. We collected a total of 18 spatial scan exposures per orbit.  The two eclipses observations from Program 13660 had a similar observing setup.

We reduced the data from both programs using a custom pipeline developed for past analyses of WFC3 data \citep[for details see][]{kreidberg14a, kreidberg14b, kreidberg15a}. Briefly, we use the optimal extraction algorithm of \cite{horne86} to extract each up-the-ramp sample (or ``stripe") separately. The stripes are then summed to create the final spectrum. For each stripe, the extraction window is 24 pixels high and centered on the stripe midpoint. We estimate the background from the median of a region of the detector that is uncontaminated by the target spectrum (rows 5-50). The typical background counts are low (10-15 photoelctrons per pixel, roughly 0.03\% of the peak counts from the target star). We note that the extracted spectrum includes flux from a nearby star, which is separated from WASP-103 by less than two pixels \citep[0.2"][]{wollert15}. We account for the contaminating flux later in the analysis.

\section{Light Curve Fits}
which orbits/data

The raw data exhibit time-dependent systematic trends typically seen in WFC3 light curves, which we correct using a systematics model of the form:

@@
